### 2017-12-12 README.Rmd
update readme

The package additionally includes methods for computing valid confidence
intervals for an inverse probability of treatment weighted (IPTW) estimator of
the average treatment effect when the propensity score is estimated via super
learning, as discussed in
[van der Laan, 2014](https://www.degruyter.com/downloadpdf/j/ijb.2014.10.issue-1/ijb-2012-0038/ijb-2012-0038.pdf).

@@

After using the `drtmle` R package, please cite the following:
  @Manual{drtmlepackage,
    title = {drtmle: Doubly-Robust Nonparametric Estimation and Inference},
    author = {David Benkeser},
    note = {R package version 1.0.0},
    doi = {10.5281/zenodo.844836},
  }
  @article{benkeser2017improved,
    year  = {2017},
    author = {Benkeser, David C and Carone, Marco and van der Laan, Mark J
      and Gilbert, Peter B},
    title = {Doubly-robust nonparametric inference on the average
      treatment effect},
    journal = {Biometrika},
    volume = {104}, number = {4},
    pages = {863–880},
    doi = {10.1093/biomet/asx053}
  }

>>>>

The package additionally includes methods for computing valid confidence
intervals for an inverse probability of treatment weighted (IPTW) estimator of
the average treatment effect when the propensity score is estimated via super
learning, as discussed in
[van der Laan (2014)](https://www.degruyter.com/downloadpdf/j/ijb.2014.10.issue-1/ijb-2012-0038/ijb-2012-0038.pdf).

@@

After using the `drtmle` R package, please cite the following:

    @Manual{drtmlepackage,
      title = {drtmle: Doubly-Robust Nonparametric Estimation and Inference},
      author = {David Benkeser},
      note = {R package version 1.0.0},
      doi = {10.5281/zenodo.844836},
    }

    @article{benkeser2017improved,
      year  = {2017},
      author = {Benkeser, David C and Carone, Marco and van der Laan, Mark J
        and Gilbert, Peter B},
      title = {Doubly-robust nonparametric inference on the average
        treatment effect},
      journal = {Biometrika},
      volume = {104}, number = {4},
      pages = {863–880},
      doi = {10.1093/biomet/asx053}
    }
